
\chapter{Electrical Engineering Foundations}


\section{Electro Magnetism}

\subsection{coulombs Law}

\subsection{Maxwells Equations}

\begin{equation}
\nabla \cdot \mathbf{D} = \rho,
\end{equation}

\begin{equation}
\nabla \cdot \mathbf{B} = 0,
\end{equation}

\begin{equation}
\nabla \times \mathbf{E} = -\frac{\partial \mathbf{B}}{\partial t},
\end{equation}

\begin{equation}
\nabla \times \mathbf{H} = \mathbf{J} + \frac{\partial \mathbf{D}}{\partial t}, 
\end{equation}

where $\mathbf{E} $ is the electric field intensity in the units of \unit{\volt\per\meter}, $\mathbf{H}$ is the magnetic field intensity in the units of \unit{\ampere\per\meter}, $\mathbf{D}$ is the electric flux (see section \ref{sec:Flux}) densities in the units of \unit{\coulomb\per\meter\squared}, and $\mathbf{B}$ is the magnetic flux density in the units of \unit{\weber\per\meter\squared} or a Tesla(\unit{\tesla}), $\mathbf{D}$ is the electric displacement and $\mathbf(B)$ is magnetic induction.
\subsection{Electric Field}
This type of electric field is based static charge, and can be thought of like gravity such that the force being exerted is all around if in a 3 d manner that diminishes with the greater range from the source.

\begin{equation}
  F = \frac{1}{4\pi\epsilon}\left( \frac{Q_{1}Q_{2}}{r^2} \right)
\end{equation}

\section{Radar}
Radar: Radio Detection And Ranging. Is simply the transmission and receiving of Radio waves. From these radio waves it is possible to determine many things about the incident target.

\subsubsection{Simple Model} 
A transmitter is to be thought as a isotropic radiator with the propagation pattern described by equation \ref{eqn:P_d}.
\begin{equation}
  P_d = \frac{P_t}{4 \pi r^2}
  \label{eqn:P_d}
\end{equation}
Where $P_d$ is the power density at some radius, $P_t$ is the power transmitted and $r$ is the radius.


\begin{equation}
  R = \frac{c \delta t}{2}
\end{equation}
\subsection{SAR}

\section{Signals and Systems}

\subsection{Adaptive Filtering}

\subsubsection{ What is an Adaptive filter}
An adaptive filter uses a Wiener Filter structure but iterates it and adjusts it such that the error is reduced and it begins to approach the ideal filter.

\begin{equation}
  h(n+1) = h(n)+\Delta h(n)
\end{equation}

\begin{equation}
  \Delta h(n) = -\gamma(\frac{d \sigma^2_{e_{\text{min}}}}{dh})
\end{equation}

\subsubsection{Applications} 
Using the ides of Wiener Filters and  Error Surfaces they can be applied inot the ideas of signal recovery in a noisey channel and noise cancellation. 

Noise cancellation
Given a the noisy signal and correlated noise we are able to filter the correlated noise such that it matches the noise of the signal and thus allows us to canel it out leaving only the signal in its place. 

 


\subsection{Sampling}

\subsection{LTI Systems}

An LTI system satisfies:
\begin{itemize}
  \item Linearity
  \item Time invariance
\end{itemize}


\subsection{Idea}
\begin{itemize}
  \item Optical PCB's
\end{itemize}

