\chapter{My Human Experience}

\section{Ideals}

\begin{enumerate}
    \item Give a shit
    \item Know my shit
    \item Don't be a shit
    \item Get shit done
\end{enumerate}

\subsection{My Confessions}
\begin{enumerate}
    \item I struggle to accept my own failures or deficiencies particularly in the area of fitness and academics. When I feel like I am deficient I will push my insecurities out onto other people such that they are they are attacking me. By doing this I avoid facing my own insecurities and am able to make myself the victim. 
    \item I do not like giving defiant answers because I do not like to be wrong. By hiding in a grey area I can never be wrong.
    \item I feel like I am drowning and everyone thinks I am lazy and not doing enough. 
    \item I am scared to leave academia, I feel like it is the only thing I am decent at. 
    \item Much of my logic and reasoning revolves around maintaining a degree of control, when that control is threatened I get very uncomfortable and at times hostile/defensive. Attempting to address this feels incredibly overwhelming as it feels so deeply rooted into who I am.
\end{enumerate}

\section{Military Leadership}
\subsection{Objective}
As a military officer my job is to manage the application of violence

\subsection{Culture}
Between branches the ideals revolve around the unit of action. In the case of the navy the unit of action is the ship, the army is the squad, and the airforce the plane. The ability for the unit of action to execute its mission is what drives the culture. In the case of the navy, for a ship to execute its mission the entre ship crew and all must act as a unified machine. Little deviation can be accepted as to ensure proper function of the ship. Hence the navy has a culture of detail driven instruction and execution. While the army being based around the squad needs to rely on the flexibility and innovation of the individuals in the squad to maintain effectiveness. Thus the army may focus more on the presentation and management of an officer as opposed to the navy's greater focus on technical ability. 



\subsection{After Action Reports}
\subsubsection{International Travel - France}
Overall the trip was a success, Some key lessons are listed below
\begin{enumerate}
    \item 
    \item 
\end{enumerate}