\chapter{Mathematical Foundations}


\section{Calculus}
\subsection{Vector Calculus}
\subsubsection{Coordinate Syestems}
    A coordinate system is a method of describing a space that function exists in. The focus will be on that of three dimensional coordinate systems; many examples exist: 
    \begin{enumerate}
        \item Cartesian(x,y,z): A point is specified by its coordinates along each basis vector relative to the origin (see Section \ref{Sec:vector Space}).
        \item Cylindrical($\rho$,$\phi$,z): A point is defined by its radial distance from the origin($\rho$), angle relative to the x direction ($\phi$), and its z coordinate.
        \begin{align}
            x &= \rho \cos\phi, \\
            y &= \rho \sin\phi, \\
            z &= z.
        \end{align}

        \begin{align}
            \rho &= \sqrt{x^2+y^2}, \\
            \phi &= \operatorname{atan2}(y,x), \\
            z &= z.
        \end{align}
        \item Spherical($\rho$,$\theta$, $\phi$): A point is defined by its radial distance from the origin ($\rho$) and its angle relative to x($\phi$) and z($\theta$). 
            \begin{align}
                x &= \rho \sin\theta \cos\phi, \\
                y &= \rho \sin\theta \sin\phi, \\
                z &= \rho \cos\theta
            \end{align}

            \begin{align}
                \rho &= \sqrt{x^2+y^2+z^2}, \\
                \phi &= \operatorname{atan2}(y,x), \\
                \theta &= \arccos\!\left(\frac{z}{r}\right).
            \end{align}
    \end{enumerate}

\subsubsection{Vectors}
\label{sec:vector}
A vector is a quantity that possesses both magnitude and direction and is commonly denoted as follows:

\begin{equation}
    \mathbf{v} = \langle a, b \rangle.
\end{equation}

Here, the vector $\mathbf{v}$ represents a vector originating at the origin and terminating at the point $(a,b)$.

Vector operations include addition, subtraction, multiplication with a scalar, dot product, and cross product.

\begin{enumerate}
    \item Vector Addition: Adding vectors involves summing the corresponding components of each vector. That is,
        \begin{equation}
            \langle x_1, y_1, z_1 \rangle + \langle x_2, y_2, z_2 \rangle
            = \langle x_1 + x_2, \; y_1 + y_2, \; z_1 + z_2 \rangle
        \end{equation}
    \item Vector Subtraction: Similar to that of vector addition with the exception that one vector has its direction reversed. 
    \item Scalar Multiplication: Multiplying a vector by a scalar scales its magnitude; it changes the vector's length but does not change its direction, except that a negative scalar reverses the direction.
    \item Dot Product:  
\end{enumerate}


\subsubsection{Equation of a Line}
The equation of a line in a 2 dimensional space is as follows 

\begin{equation}
    y = a*x+b,
\end{equation}

where $a$ is the slope or the ratio of change relating a change in $x$ to a change in $y$ and $b$ is a starting value of y when x is at the origin. 

In order to calculate a line in 3 dimensions three components are needed: a known point on the line($\vec{a_0} = \langle x_0, y_0, z_0\rangle$), a arbitrary point on the line($\vec{a} = \langle x, y, z\rangle$) and a vector parallel to the line($\vec{v}$). With these components and the vector operation noted in Section \ref{sec:vector} the equation is as follows: 

\begin{align}
    \vec{b} &= \vec{a_0} - \vec{a}, \\
    \vec{a} &= \vec{a_0} +  \vec{b}, \\
    \vec{a} &= \vec{a_0} + t * \vec{v}.
\end{align} 
Such that, $t$ is a arbitrary scalar multiplied with the parallel vector $\vec{v}$. This can be further expanded to 

\begin{align}
    \vec{a} &= \vec{a_0} + t * \vec{v}, \\
    \vec{a} &= \langle x_0, y_0, z_0\rangle + t * \langle x_v, y_v, z_v\rangle, \\ 
    \vec{a} &= \langle x_0 + t*x_v, y_0+ t*y_v, z_0+ t*z_v\rangle
\end{align}

Note that this equation will generate a vector that points to all points on the line as determined by the value of $t$ and can be though of as a laser pointer following the line. 

\subsubsection{Equation of a Plane}


\subsubsection{Flux}
\label{sec:Flux}


\section{Linear Algebra}

\subsection{Vector Spaces}
\label{sec:vector Space}


\subsection{Why This Matters}
Linear algebra underpins signal spaces, optimization, and estimation theory.
